A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-06-05 bioc-workflow.Rmd
adjust fig width

```{r plot2Drep}
par(mfrow = c(1, 2))
plot2D(hl[hl$replicate == 1], fcol = "SVM.marker.set", main = "Replicate 1")
plot2D(hl[hl$replicate == 2], fcol = "SVM.marker.set", mirrorY = TRUE, main = "Replicate 2")
```

@@

```{r visualiseOpt, eval=FALSE}
(best <- getParams(params))
plot(params)
levelPlot(params)
```
```{r visualiseOptHide, echo=FALSE}
grid.arrange(plot(params), levelPlot(params), ncol = 2)
```

>>>>

```{r plot2Drep, fig.width = 12}
par(mfrow = c(1, 2))
plot2D(hl[hl$replicate == 1], fcol = "SVM.marker.set", main = "Replicate 1")
plot2D(hl[hl$replicate == 2], fcol = "SVM.marker.set", mirrorY = TRUE, main = "Replicate 2")
```

@@

```{r visualiseOpt, eval=FALSE}
(best <- getParams(params))
plot(params)
levelPlot(params)
```
```{r visualiseOptHide, echo=FALSE, fig.width = 12}
grid.arrange(plot(params), levelPlot(params), ncol = 2)
```
